### 2015-12-31 Projects/DelCo_2012/Report/DelCo_2012.tex
edits to cafs paper

\chapter*{\centering Abstract}
Traditionally, fire fighting suppression operations have been conducted from the interior of the structure as a means to reduce water damage, manage the ``thermal balance'', and limit fire damage to structures. In current fire fighter training manuals, it is stated that these operations must be coordinated with the ventilation operations. However guidance on that coordination has been limited. Previous research and examinations of line of duty deaths have shown that ventilation events occurring with fire fighters in the structure prior to suppression have led to tragic results. One means of reducing the possibilities of this occurrence would be to begin to extinguish the fire prior to entering the structure. In effect, an offensive, exterior fire attack, in which water is directed into the structure from the exterior to cool the fire gases and reduce the heat release rate of the fire, prior to the fire fighters entering the building. The major concern with this type of operation is the potential harm that might occur to people trapped in the structure or the amount of water damage to the structure. Additionally, the type of suppression agent can affect the fire behavior within the structure. The suppression agent is the main focus of this study to determine whether or not compressed air foam systems provide any significant benefit to the traditional water application. Therefore, measurements are needed to document the changes of the thermal environment within the structure due to interior and exterior fire suppression tactics over all types of suppression agents. This report will focus on water distribution and fire suppression experiments conducted to develop a baseline for the interior fire suppression using both water and compressed air foam application.
\pagenumbering{gobble}

>>>>

\chapter*{\centering Abstract}

\pagenumbering{gobble}
